\href{http://www.libsdl.org/}{\tt http\+://www.\+libsdl.\+org/}\hypertarget{index_intro_sec}{}\section{Introduction}\label{index_intro_sec}
Simple Direct\+Media Layer is a cross-\/platform development library designed to provide low level access to audio, keyboard, mouse, joystick, and graphics hardware via Open\+GL and Direct3D. It is used by video playback software, emulators, and popular games including Valve\textquotesingle{}s award winning catalog and many Humble Bundle games.

S\+DL officially supports Windows, Mac OS X, Linux, i\+OS, and Android. Support for other platforms may be found in the source code.

S\+DL is written in C, works natively with C++, and there are bindings available for several other languages, including C\# and Python.

This library is distributed under the zlib license, which can be found in the file \char`\"{}\+C\+O\+P\+Y\+I\+N\+G.\+txt\char`\"{}.

The best way to learn how to use S\+DL is to check out the header files in the \char`\"{}include\char`\"{} subdirectory and the programs in the \char`\"{}test\char`\"{} subdirectory. The header files and test programs are well commented and always up to date. More documentation and F\+A\+Qs are available online at\+: \href{http://wiki.libsdl.org/}{\tt http\+://wiki.\+libsdl.\+org/}

If you need help with the library, or just want to discuss S\+DL related issues, you can join the developers mailing list\+: \href{http://www.libsdl.org/mailing-list.php}{\tt http\+://www.\+libsdl.\+org/mailing-\/list.\+php}

Enjoy! Sam Lantinga (\href{mailto:slouken@libsdl.org}{\tt slouken@libsdl.\+org}) 